---
title: "Presentation Ninja"
subtitle: "References with xaringan"
author: "Joseph Casillas"
date: "Last update: `r Sys.Date()`"
output: xaringan::moon_reader
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

# Bib setup

```{r}
source(here::here("helper.R"))
library(RefManageR)
BibOptions(check.entries = FALSE, 
           bib.style = "authoryear", 
           style = "markdown",
           dashed = TRUE)
file.name <- system.file("Bib", 
                         "biblatexExamples.bib", 
                         package = "RefManageR")
bib <- ReadBib(file.name)
```
---

# Citaion examples

1. Standard citation, single author:  
`r AutoCite(bib, "wilde")`

2. Multiple citations `r AutoCite(bib, "bertram")` on a single line `r AutoCite(bib, "kastenholz")`.

3. Inline citation:  
`r Citet(bib, "iliad")` said this and this. 

4. More than two authors:  
`r AutoCite(bib, "vazques-de-parga")`

5. More than two authors inline:  
`r Citet(bib, "springer")` talk about things. 
`r Citet(bib, "massa")` has great ideas.

```{r}
# 6. 'NoCite' function to include references in bib that 
#    don't appear in text
NoCite(bib, c("knuth:ct:a", "aristotle:poetics", "herrmann"))
```

---

# References (all on one page)

```{r, results='asis', echo=FALSE, warning=FALSE}
PrintBibliography(bib)
```

---

# References (split up)

```{r, results='asis', echo=FALSE, warning=FALSE}
print_bib_rmd(bib, start = 1, stop = 6)
```

---

# References II (split up)

```{r, results='asis', echo=FALSE, warning=FALSE}
print_bib_rmd(bib, start = 7, stop = 10)
```

